\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-03 paper.tex
from overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
This paper addresses security challenges in multi-robot systems (MRS) where adversaries may compromise robot control, risking unauthorized access to forbidden regions. We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability} constraints for enhanced security. This ensures that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations. The reachability constraint uses ellipsoidal over-approximation for efficient intersection checking and gradient computation. To enhance system resilience and tackle feasibility challenges, we also introduce \emph{sub-teams}. These cohesive units replace individual robot assignments along each route, enabling redundant robots to deviate for co-observations across different trajectories, securing multiple sub-teams without requiring modifications. We formulate the \emph{cross-trajectory co-observation} plan by solving a network flow coverage problem on the checkpoint graph generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks. We demonstrate the effectiveness and robustness of our proposed algorithm, which significantly strengthens the security of multi-robot systems in the face of adversarial threats.
\end{abstract}
\begin{IEEEkeywords}
  Multi-robot system, cyber-physical attack, trajectory optimization, reachability analysis, network flow
\end{IEEEkeywords}

@@

{\news %\zyang{this version right?} To avoid confusion, \zyanghl{Can i do this? since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} 
Our strategy is based on the following concept:
\begin{definition}
The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ at which a robot is co-observed by its teammates, and where it can leave or join a new team.
\end{definition}
For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. %, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding location and time for checkpoint $v_{pi}$.
To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
\begin{remark}
  A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
  \end{remark}
}
{\news \zyang{Any better ways since $V_c, E$ are all introduced later?, also will $V_p$ and $V_q$ cause confusion?} 
% The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is illustrated as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ are union of checkpoints $V_p$ and connection verticies $V_c$, $E_{q} = E_{t} \union E_{c}$ are union of trajectory edges $E_t$ and connection edges $E_c$ (introduced later in \cref{sec:cross-trajectory}). Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph. This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where verticies $V = (\union_p V_p) \union V_c$ are a subset of waypoints on the planned trajectory, and edges $E_{q} = E_{t} \union E_{c}$ represents feasible paths connecting $V_q$. Specifically,
\begin{description}
  \item[$V_p$]: Checkpoints where additional robots are required for security through co-observation.
  \item[$E_t$]: Trajectory edges representing the original planned path of the primary robot.
  \item[$E_c$]: Cross-trajectory edges with at least one endpoint as a checkpoint, representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support.
  \item[$V_c$]: Connection vertices representing non-checkpoint locations linked via $E_c$.
\end{description}

The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G$. To satisfy security requirements, every checkpoint $V$ must be visited by at least one flow.This formulation reduces the co-observation problem to finding valid flow patterns in $G$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions.
}

@@

Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$. The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur during trajectory switches.  
%\end{remark}

\begin{figure}[htbp]
    \centering
  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0cm, clip, valign=c]{two_edges}}
  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0.2cm, clip, valign=c]{security_graph}}
  \caption{{\news (\ref{fig:two-edges}) Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$. (\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$. Virtual source $v^{+}$ and sink $v^{-}$ are added to be used later in planning problem.}}  
\end{figure}

@@

We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone (ignoring, for the moment, any timing constraint). 
More precisely, \new{for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.}
Then, to prune these trees, we consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints. This is done by calculating the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path. Two types of connecting nodes can be found.

@@

For each trajectory $r\neq p$, we define the \emph{latest departure node} $v_{ld}=(q_{r}(t^{d}_r),t^{d}_r)$ as the departure node characterized by the maximum $t^{d}_r$ discovered.
% $t^{d}_r$ is designated as the \emph{latest departure time}.
\end{description}
% For each $v_{p} \in V_{p}$, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$. Examples are shown in \cref{fig:two-edges}.
{\news $V_c$ is the collection of all the latest departure and earliest arrival nodes (if they are not identified as checkpoints already), and the corresponding paths are added as cross-trajectory edges $E_q$. A toy example is shown in \cref{fig:two-edges}.}

@@

%With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
\new{Let $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ represent the set of all vertices found in~\cref{sec:security-checkpoint,sec:cross-traj-edges}. We group these verticies by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$. For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing corresponding segment of the planned trajectory. Examples are shown in \cref{fig:security-graph-generate}. }

@@

{\news To formulate the problem as a network multi-flow problem, we augment the checkpoint graph to a flow graph. A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node is added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$. Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v_{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v_{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}

%The goal is to find paths in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
The path of a robot $k$ all starts from $v^{+}$ and ends at $v^{-}$, and are represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$. The planning problem can be formulated as a path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \Cref{rmk:revised-security}). %Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.

@@

The first term in the cost \eqref{eq:flow-cost} represents the total number of robot used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms. \eqref{eq:FlowBalanceConstraint} is the flow conservation constraint to ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$). \eqref{eq:FlowCoverage} is the flow coverage constraints to ensures that all security checkpoints $ \{V^{s}_{p}\}$ have been visited co-observed. The security graph $G_{q}$ is acyclic, making this problem in complexity class $P$, thus, can be solved in polynominal time \cite{1702662}.

\subsection{Co-observation performance}
Notice that problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  %Additionally, for a fixed number of robots $\cK \geq N_{p}$, 
It is possible for the resulting flows to have a subset of flows $F_{e} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$; these flow will not increase the cost and can be discarded from the solution.

The constant $\rho$ selects the trade-off between the number of surveillance robots and security performance. An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots. In order to identify the minimum number of robots necessary, we propose an iterative approach where we start with $\cK=1$ and gradually increases it until $F$ contains an empty flow, indicating the point where further robot additions do not improve performance.

@@

\appendix
{\news
\subsection{Transformation of reachability ellipsoid to canonical frame}\label{apx:transformation}
The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, with foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ defined as
$q^\cE_1=\bmat{c & 0 & 0}\transpose, q^\cE_2=\bmat{-c & 0 & 0}\transpose$, and semi-axis distance $c=\frac{\norm{q_2-q_1}}{2}$.
\begin{definition}
  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$, $b$ represent the lengths of the major axes.
\end{definition}
\begin{lemma}
The original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
   \begin{equation}\label{eq:ellpsoid from canonical}
     \Fframe{E}(q) = (q-o_\cE)\transpose H\transpose Q H (q-o_\cE) - 1
     \end{equation}
\end{lemma}
\begin{proof}
    The claim follows by substituting  \eqref{eq:transformations} into \eqref{equ:standard-ellipse}, and from the definition of $R$ and $o$.
\end{proof}
\subsection{Householder rotations}\label{sec:householder}
\new{We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \Cref{sec:reachability,sec:ellipse-region-constraint}. This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}. 
% With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection). 
We call our version of the operator a \emph{Householder rotation}. In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.}
\begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
  % \begin{equation}
  %   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
  % \end{equation}
the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
  \begin{equation}\label{eq:H definition}
    H(\nu_1,\nu_2) = 2 u u\transpose-I.
  \end{equation}
\end{definition}
Here $H$ is a rotation mapping $\nu_1$ to $\nu_2$, as shown by the following.
\begin{proposition}\label{prop:HProperty}
  The matrix $H$ has the following properties:
  \begin{enumerate}
  \item It is a rotation, i.e.
    \begin{enumerate}
    \item\label{it:orthonormality} $H\transpose H=I$;
    \item\label{it:determinant} $\det(H)=1$.
    \end{enumerate}
  \item\label{it:transformation} $\nu_2=H \nu_1$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  For subclaim~\ref{it:orthonormality}:
  \begin{equation}
    H\transpose H=H^2=4uu\transpose u u\transpose - 4uu\transpose +I^2=I,
  \end{equation}
  since $u\transpose u=1$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We address security challenges in multi-robot systems (MRS) where adversaries may take control of compromised robots to gain unauthorized physical access to forbidden regions. We propose a novel multi-robot optimal planning algorithm that integrates mutual observations and introduces \emph{reachability constraints} and \emph{co-observations} between robots to enhance security. Our formulation can guarantee that, even with adversarial movements, compromised robots cannot breach forbidden regions without missing scheduled co-observations. We use ellipsoidal over-approximations to reachability regions for efficient intersection checking and gradient computation. Furthermore, to enhance system resilience and tackle feasibility challenges, we introduce the notion of \emph{sub-teams}; these cohesive units replace individual robots along each route; we plan \emph{cross-trajectory co-observation} that use redundant robots to switch between routes, securing multiple sub-teams without requiring modifications to the plans. We formulate cross-trajectories plans by solving a \emph{network-flow vertex path coverage problem} on the \emph{checkpoint graph} generated from the original unsecured MRS trajectories, providing the same security guarantees against plan-deviation attacks. We demonstrate the effectiveness and robustness of our proposed algorithm through simulations, which significantly strengthen the security of multi-robot systems in the face of adversarial threats.
\end{abstract}
\begin{IEEEkeywords}
  Multi-robot system, cyber-physical attack, trajectory optimization, reachability analysis, network flow
\end{IEEEkeywords}

@@

{\news %\zyang{this version right?} To avoid confusion, \zyanghl{Can i do this? since qp is a matrix}{let $q_{p}(t)\in \real{m}$ denotes the reference waypoint for sub-team $p$ at time $t$.} 
Our strategy is based on the following concept:
\begin{definition}
The $i$-th \emph{checkpoint} $v_{pi}=(q_{p},t_{i})$ for sub-team $p$ is defined as a location $q_{pi}=q_{p}(t_i)$ and time $t_{i}$ at which a robot is co-observed by its teammates, and where it can leave or join a new team.
\end{definition}
For simplicity, let $\cI_{v_{i}}$ denote the sub-team to which $v_{i}$ belongs. %, and $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding location and time for checkpoint $v_{pi}$.
To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
\begin{remark}
  A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
  \end{remark}
}
{\news \zyang{Make this a definition} 
% The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is illustrated as a directed \emph{checkpoint graph} $G{q}=(V_{q}, E_{q})$, where $V_{q} = V_p \union V_c$ are union of checkpoints $V_p$ and connection verticies $V_c$, $E_{q} = E_{t} \union E_{c}$ are union of trajectory edges $E_t$ and connection edges $E_c$ (introduced later in \cref{sec:cross-trajectory}). Inspired by~\cite{yu2013multi}, additional robots in the sub-team are treated as flows in the checkpoint graph. This transforms the co-observation planning problem into a network multi-flow problem, solvable with general Mixed-Integer Linear Programming techniques.
The planned trajectory $\{q_p\}_{p=1}^{N_p}$ is represented as a directed \emph{checkpoint graph} $G=(V, E)$, where verticies $V = (\union_p V_p) \union V_c$ are a subset of waypoints on the planned trajectory, and edges $E = E_{t} \union E_{c}$ represents feasible paths connecting $V$. Specifically,
\begin{description}
  \item[Checkpoints $V_p$] where additional robots are required for security through co-observation.
  \item[Tranectory edges $E_t$] representing the original planned path of the primary robot.
  \item[Connection vertices $V_c$] representing non-checkpoint locations linked via $E_c$.
  \item[Cross-trajectory edges $E_c$] representing feasible paths where robots deviate from the original trajectory to join other teams or provide co-observation support, at least one endpoint be a checkpoint. 
\end{description}

The co-observation planning problem is transformed into a network multi-flow problem where the additional robots treated as flows traveling through $G$. To satisfy security requirements, every checkpoint $V$ must be visited by at least one flow. This formulation reduces the co-observation problem to finding valid flow patterns in $G$, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions. \rtron{Add some references to MILP for multi-flow path planning}
}

@@

Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$. The cross-trajectory edges must also adhere to reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden regions can occur {\news while switching trajectories}.  
%\end{remark}

\begin{figure}[htbp]
    \centering
  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0cm, clip, valign=c]{two_edges}}
  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0.2cm, clip, valign=c]{security_graph}}
  \caption{{\news (\ref{fig:two-edges}) Latest departure node $q^{d}_{b}$ found for $v_{r1}$ and earliest arrival node $q^{a}_{b}$ found for $v_{r3}$. (\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}}  
\end{figure}

@@

We first find trees of feasible paths between each security checkpoint and all other trajectories using position information alone (ignoring, for the moment, any timing constraint). 
More precisely, \new{for each checkpoint $v_p \in \union_p V_p$, we use \rrtstar~ to find all feasible, quasi-optimal paths from $q_{v_p}(t_{v_p})$ to all the waypoints $\{q_{r}(t_{{r}_{i}})\}$ on the reference trajectories of all other sub-teams $\cI_{r} = \cI \setminus \cI_{p}$.}
Then, to prune these trees, we consider the time needed to physically travel from one trajectory to the other while meeting other robots at the two endpoints. This is done by calculating the minimal travel time $t_{\textrm{path}}=\texttt{Cost}(q)/v_{max}$ for a robot to traverse each path. Two types of connecting nodes can be found.

@@

For each trajectory $r\neq p$, we define the \emph{latest departure node} $v_{ld}=(q_{r}(t^{d}_r),t^{d}_r)$ as the departure node characterized by the maximum $t^{d}_r$ discovered.
% $t^{d}_r$ is designated as the \emph{latest departure time}.
\end{description}
% For each $v_{p} \in V_{p}$, all the latest departure and earliest arrival nodes are added as vertices $V_q = V_{p} \union \{v_{ea}, v_{ld}\}$, and the corresponding paths are added as cross-trajectory edges to $E_{q}$. Examples are shown in \cref{fig:two-edges}.
{\news The set $V_c$ contains all the \emph{latest departure} and \emph{earliest arrival} nodes (if they are not identified as checkpoints already); the corresponding paths are added as cross-trajectory edges $E_q$. A toy example is shown in \cref{fig:two-edges}.}

@@

%With vertices $V_{q}$ and cross-trajectory edges $E_{q}$ found in Algorithm \ref{alg:cross-trajectory-edges}, we can construct a security graph $G_{q}$. 
\new{\rtronhl{We already defined this}{Let $V =\{ v^i_p,\dots\}_{p=1}^{N_p}$ represent the set of all vertices} found in~\cref{sec:security-checkpoint,sec:cross-traj-edges}. We group these verticies by sub-teams and arrange them in ascending order of their timestamps $t_{v^i_{p}}$. For each sub-team, consecutive vertices $v^i_{p}$ and $v^{i+1}_{p}$ are connected by adding \emph{in-trajectory edges} $\{(v^i_{p}\rightarrow v^{i+1}_{p})\}$ to $E_q$, representing corresponding segment of the planned trajectory. Examples are shown in \cref{fig:security-graph-generate}. }

@@

{\news To formulate the problem as a network multi-flow problem, we augment the checkpoint graph to a flow graph. A \emph{virtual source} node $v^{+}$ and a \emph{virtual source} node is added to the vertices $V= (\union_p V_p) \union V_c \union \{v^{+},v^{-}\}$. Additional directed edges from $v^{+}$ to all the start vertices, and from all end vertices to $v^{-}$ are added $E = E_{q} \union \{(v^{+},v^{0}_{p})\}_{p} \union \{( v^{T}_{p},v^{-})\}_{p}$ with $v^0_p$ and $v^T_p$ representing the start and end vertices of sub-team $\cI_p$ (dashed arrows in~\cref{fig:example-cross-traj}).}

%The goal is to find paths in $G$ for all the cross-trajectory robots that starts from the virtual source $v^{+}$ and ends in the virtual sink $v^{-}$.
The path of a robot $k$ all starts from $v^{+}$ and ends at $v^{-}$, and are represented as a flow vector $\vf^{k} = \{ f^{k}_{ij} \}$, where $f^{k}_{ij} \in \{1,0\}$ is an indicator variable representing whether robot $k$'s path contains the edge $v_{i}\to v_{j}$. 
The planning problem can be formulated as a vertex path cover problem on $G_{q}$, i.e., as finding a set of paths $F=[\vf_{1},\dots, \vf_{\cK}]$ for cross-trajectory robots such that every checkpoint in $\union_p V_{p}$ is included in at least one path in $F$ (to ensure co-observation at every checkpoint as required by \Cref{rmk:revised-security}). %Additionally, to encourage the robots' exchange between different sub-teams, cross-trajectory co-observations should be preferred compared to co-observation within the same team.

@@

The first term in the cost \eqref{eq:flow-cost} represents the total number of robot used, and the second term represents the overall co-observation performance (defined as the total number of cross-trajectory edges taken by all flows beyond the regular trajectory edges); the constant $\rho$ is a manually selected penalty parameter to balance between the two terms. 
The flow conservation constraint \eqref{eq:FlowBalanceConstraint} ensures that the amount of flow entering and leaving a given node $v$ is equal (except for $v^{+}$ and $v^{-}$). The flow coverage constraint \eqref{eq:FlowCoverage} ensures that all checkpoints $ \{V^{s}_{p}\}$ have been visited and can support a co-observation. The checkpoint graph $G$ is acyclic, placing this problem in complexity class $P$; thus, it can be solved in polynominal time \cite{1702662}.

\subsection{Co-observation performance}
The network flow problem \eqref{eq:flow-coverage-problem} is guaranteed to have a solution for $\cK=N_{p}$ where all $\cK$ robots follows the reference trajectory ($f^{k}_{ij}=1, \forall \cI_{v_{i}}=\cI_{v_{j}}=k$).  %Additionally, for a fixed number of robots $\cK \geq N_{p}$, 
It is possible for the resulting flows to have a subset of flows $F_{e} \in F$ that is empty, i.e. $f_{ij}=0, \forall (v_{i},v_{j})\in E$, $f\in F_{e}$; these flow will not increase the cost and can be discarded from the solution.

The constant $\rho$ selects the trade-off between the number of surveillance robots and security performance. An increase in robots generally enhances security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots. In order to identify the minimum number of robots necessary, we propose an iterative approach in which we start with $\cK=1$ and gradually increase it until $F$ contains an empty flow, indicating the point where further additions of robots do not improve performance.

@@

\appendix
{\news
\subsection{Transformation of a reachability ellipsoid to canonical frame}\label{apx:transformation}
The ellipse $\cE$ expressed in $\cF_\cE$ is given by $\Eframe{\cE}=\{\Eframe{q}\in\real{m}:d(q^\cE_1,\Eframe{q})+d(\Eframe{q},q^\cE_2)<2a\}$, with foci $q^\cE_1,q^\cE_2$ in $\cF_\cE$ defined as
$q^\cE_1=\bmat{c & 0 & 0}\transpose, q^\cE_2=\bmat{-c & 0 & 0}\transpose$, and semi-axis distance $c=\frac{\norm{q_2-q_1}}{2}$.
\begin{definition}
  The \emph{reachability ellipsoid $\cE$ in the canonical frame} is defined as as the zero level set of the quadratic function
  \begin{equation}\label{equ:standard-ellipse}
    \Eframe{E}(\Eframe{q}) = \Eframe{q}\transpose Q \Eframe{q} - 1
  \end{equation}
  where
  \begin{equation}
    Q = \diag(a^{-2},b^{-2},b^{-2}),
  \end{equation}
  and $b = \sqrt{a^2-c^2}$.
  The ellipse parameters $a$, $b$ represent the lengths of the major axes.
\end{definition}
\begin{lemma}
The original ellipse $\cE$ in $\cF$ can be expressed as the zero level set of the quadratic function
   \begin{equation}\label{eq:ellpsoid from canonical}
     \Fframe{E}(q) = (q-o_\cE)\transpose H\transpose Q H (q-o_\cE) - 1
     \end{equation}
\end{lemma}
\begin{proof}
    The claim follows by substituting  \eqref{eq:transformations} into \eqref{equ:standard-ellipse}, and from the definition of $R$ and $o$.
\end{proof}
\subsection{Householder rotations}\label{sec:householder}
\new{We define a differentiable transformation to a canonical ellipse that is used in the derivation of the reachability constraints in \Cref{sec:reachability,sec:ellipse-region-constraint}. This transformation includes a rotation derived from a modified version of Householder transformations \cite{householder1958unitary}. 
% With respect to the standard definition, our modification ensures that the final operator is a proper rotation (i.e., not a reflection). 
We call our version of the operator a \emph{Householder rotation}. In this section we derive Householder rotations and their differentials for the 3-D case; the 2-D case can be easily obtained by embedding it in the $z=0$ plane.}
\begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
  % \begin{equation}
  %   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
  % \end{equation}
the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
  \begin{equation}\label{eq:H definition}
    H(\nu_1,\nu_2) = 2 u u\transpose-I.
  \end{equation}
\end{definition}
Here $H$ is a rotation mapping $\nu_1$ to $\nu_2$, as shown by the following.
\begin{proposition}\label{prop:HProperty}
  The matrix $H$ has the following properties:
  \begin{enumerate}
  \item It is a rotation, i.e.
    \begin{enumerate}
    \item\label{it:orthonormality} $H\transpose H=I$;
    \item\label{it:determinant} $\det(H)=1$.
    \end{enumerate}
  \item\label{it:transformation} $\nu_2=H \nu_1$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  For subclaim~\ref{it:orthonormality}:
  \begin{equation}
    H\transpose H=H^2=4uu\transpose u u\transpose - 4uu\transpose +I^2=I,
  \end{equation}
  since $u\transpose u=1$.
